---
title:           Week 2
author:          Dennis Wollersheim
date:            "`r format(Sys.time(), '%d %B, %Y')`"
linkcolor:       cyan
citecolor:       grey
output:
  pdf_document:
    highlight:   zenburn
---


```{r setup1, include=FALSE}
source('_drake.R')
```



\tableofcontents


# Agenda

## Introductions
 - What is your Name, successes with R or data this week

## Challenges
  - what are your challenges with data this week? This month?  All time?


# This week - dealing with big data
  - structure
  - reproducible
  - don't do anything twice


# Exploration of the PBS / MBS dataset

 - 10 years of PBS data, 20 years of MBS data

 - ATC drug codes and drug categories also included

```{r}
loadd( df_pbs )

df_pbs %>%
  ggplot( aes( supply_date, fill= atc_meaning) ) +
  geom_bar()

df_pbs %>%
  mutate( year = year( supply_date) ) %>%
  ggplot( aes( year, fill= atc_meaning) ) +
  geom_bar()

df_pbs %>%
  mutate( year = year( supply_date) ) %>%
  count( year, atc_meaning) %>%
  ggplot( aes( x=year, y=n, color= atc_meaning) ) +
  geom_point() +
  geom_line()


```
